---
title: "Bird Joins"
author: "Grace Lewin"
date: "8/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(lubridate)
```

```{r}
bird_observations <- read_csv(here("data", "52_pp52_birds_1.csv"))

sites <- read_csv(here("data", "52_pp52_sites_1.csv"))

surveys <- read_csv(here("data", "52_pp52_surveys_1.csv"))

taxalist <- read_csv(here("data", "52_pp52_taxalist_1.csv"))

birds_subset <- bird_observations %>% 
  filter(species_id %in% c("BHCO", "RWBL")) %>% 
  filter(site_id %in% c("LI-W", "NU-C"))
```

## Left Join Practice

```{r}
birds_left <- birds_subset %>% 
  left_join(sites, by = "site_id") %>% 
  left_join(taxalist, by = "species_id")
```

## Full Join practice

I expect a full_join() between birds_subset and sites to give a data frame with all the information from both data frames included. Even if there is not a match between the two data frames.

```{r}
birds_full <- full_join(birds_subset, sites, by = "site_id")
```


## Inner join practice

i expect an inner_join() between birds_subset and taxalist to contain a data frame that keeps the information if there is a key match between the two data frames.

```{r}
birds_inner <- inner_join(birds_subset, taxalist, by = "species_id")

birds_taxa_left <- left_join(birds_subset, taxalist, by = "species_id")
```


## Task 2: Data Wrangling and visualization with birds

```{r}
bird_observations <- bird_observations %>% 
  rename(bird_obs_notes = notes)

bird_subset_2 <- bird_observations %>% 
  left_join(taxalist, by = "species_id") %>% 
  left_join(sites, by = "site_id") %>% 
  left_join(surveys, by = c("site_id", "survey_id")) %>% 
  select(survey_date, common_name, park_name, bird_count) %>% 
  mutate(survey_month = lubridate::month(survey_date)) %>% 
  mutate(survey_month = as.factor(survey_month)) %>% 
  relocate(survey_month, .after = survey_date)

num_birds_park_month <- bird_subset_2 %>% 
  group_by(park_name, survey_month) %>% 
  summarize(count = n())

birds_subset_2_parks_subset <- bird_subset_2 %>% 
  filter(park_name %in% c("Lindo", "Orme", "Palomino", "Sonrisa"))
  
```





